### 2020-07-28 draft.Rmd
add variance plot by group with outliers removed

>>>>

```{r variance-by-group-quantile}

skewc = treated %>%
  group_by(group) %>%
  filter(balchange < quantile(balchange, 0.99)) %>%
  ggplot(aes(balchange, y = group, color = group)) +
  geom_point(alpha=0.2) +
  scale_x_continuous(labels = scales::comma) +
  labs(title = "Variance by treatment having removed significant outliers",
       x = "Change in balance (Philippine Peso)",
       y = NULL) +  
  theme_minimal()

skewc
rm(skewc)
